---
title: "Technology Assessment"
author: "Ignatius Menzies"
date: "5 June 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source('src/relative_difference.R')
```

```{r}
mean(boot_slopes_06_13$p_value)
mean(boot_slopes_06_13$adj_r_square)
mean(boot_slopes_06_13$slope)
mean(boot_slopes_06_13$intercept)

summary(boot_slopes_06_13)



# plot(census_prob$probability, census_prob$perc_difference_06_13)

# census_prob[order(-perc_difference_06_13),]

# outlier_values <- boxplot.stats(census_prob$perc_difference_06_13)$out  # outlier values.
# boxplot(census_prob$perc_difference_06_13, main="Percent difference between censuses", boxwex=0.1)
# mtext(paste("Outliers: ", paste(outlier_values, collapse=", ")), cex=0.6)

mean(boot_slopes_13_18$p_value)
mean(boot_slopes_13_18$adj_r_square)
mean(boot_slopes_13_18$slope)
mean(boot_slopes_13_18$intercept)

summary(boot_slopes_13_18)

```

> mean(boot_slopes_06_13$rho)
[1] -0.253688
> mean(boot_slopes_13_18$rho)
[1] -0.08786565


> sd(boot_slopes_06_13$rho)
[1] 0.01707973
> sd(boot_slopes_13_18$rho)
[1] 0.0169028

> summary(boot_slopes_06_13)
    p_value               rho         
 Min.   :0.000e+00   Min.   :-0.3036  
 1st Qu.:0.000e+00   1st Qu.:-0.2652  
 Median :1.000e-14   Median :-0.2532  
 Mean   :4.814e-11   Mean   :-0.2537  
 3rd Qu.:1.600e-13   3rd Qu.:-0.2420  
 Max.   :8.855e-08   Max.   :-0.1767 
> summary(boot_slopes_13_18)
    p_value               rho          
 Min.   :0.0000078   Min.   :-0.14655  
 1st Qu.:0.0025279   1st Qu.:-0.09929  
 Median :0.0078174   Median :-0.08750  
 Mean   :0.0169185   Mean   :-0.08787  
 3rd Qu.:0.0210387   3rd Qu.:-0.07594  
 Max.   :0.3657425   Max.   :-0.02981  
 
 2001 and 1996 census use different occupation classification (NZSCO99), plus 1996 data tables download links point to the wrong file :( 
 
 